---
title: "Lab2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Problem 1

```{r}
x = c(12,8,5,7,23,56,14,9,33,28)
mean(x)
min(x)
max(x)
TestNum<-min(x):max(x)
SumDev<-c()
for (i in TestNum) {
  SumDev[i]<-sum(x-i)
}
SumDev
plot(abs(SumDev))
```



##Problem 2

```{r}
# Variance R formula
var(x)

#Variance one line formula
var2<-(sum((x-mean(x))^2))/(length(x)-1)
var2

#variance multi line formula
Dev<-x-mean(x)
Dev2<-Dev^2
sum2<-sum(Dev^2)
Length<-length(x)
Var3<-sum2/(Length-1)
Var3

#SD R formula
sd(x)

#SD formula
SD2<-sqrt((sum((x-mean(x))^2))/(length(x)-1))
SD2
```

##Problem 3

```{r}
library(dplyr)
library(ggplot2)
sections<-c("morning","afternoon","evening")
grades<-c(85,90,93)
data<-data.frame(sections,grades)
data

ggplot(data, aes(x=sections,y=grades))+
  geom_bar(stat="identity")
```
##Problem 4

```{r}
instructors<-c("one","one","one","two","two","two")
sections<-c("morning","afternoon","evening","morning","afternoon","evening")
grades<-c(75,78,80,88,76,63)
data<-data.frame(instructors,sections,grades)
data

ggplot(data, aes(x=sections,y=grades,group=instructors,fill=instructors))+
  geom_bar(stat="identity", position="dodge")
```
##Problem 5

```{r}

WHR<-read.table("open_data/WHR2018.csv",
                             sep = ",",
                             header = TRUE )
WHR

HLEmean<-WHR %>%
  filter(year>=2010,
         year<=2015)%>%
  group_by(year) %>%
  summarize(HLEmean2=mean(Healthy.life.expectancy.at.birth, na.rm=TRUE))

knitr::kable(HLEmean)
ggplot(HLEmean, aes(x=year,y=HLEmean2))+
  geom_bar(stat="identity")
```

##Problem 6

```{r}

HLEmean<-WHR %>%
  filter(year>=2010,
         year<=2015)%>%
  group_by(year) %>%
  summarize(HLEmean2=mean(Healthy.life.expectancy.at.birth, na.rm=TRUE),
            HLEsd= sd(Healthy.life.expectancy.at.birth, na.rm=TRUE))

knitr::kable(HLEmean)
ggplot(HLEmean, aes(x=year,y=HLEmean2))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin = HLEmean2 - HLEsd,
                    ymax = HLEmean2 + HLEsd),
                width = .25)
```

Confidence: I tried to do question 1, 2, and 6 without looking at the solutions, although I did need to refer back to the lecture video. For question 1, I'm not sure why I get 'N/A' in my output. I need to continue to troubleshoot this. For question 2, I was unable to figure out how to do the median or mode, and I believed I did the variance/SD correctly until I looked at your solution video, and noticed that you used 'function()' which I did not. When you instruct to 'write an R function', does it mean to use 'function()'? I suppose I just wrote a formula which is probably incorrect. I needed a lot more help with the rest of the problems.
1 = 80, 2 = 50, 3 = 0, 4 = 0, 5 = 0, 6 = 80