---
title: "Lab7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Question 1

```{r}
test_results<-binom.test(x = 30,
           n = 50,
           p = .5,
           alternative='greater')

test_results$p.value


```
Since the p-value is .101, we can conclude that there is a 10.1% chance that this test-score can be produced by the test-taker randomly guessing on each question.

##Question 2

```{r}
binom.test(x = 385,
           n = 700,
           p = .5,
           alternative='greater')


```
700 questions is sufficient for ~.5 person per 100 to obtain a score of over 55% by chance.

##Question 3

```{r}
rbinom(n=rep(1,10),size=1,prob=c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25))
test<-replicate(10000,rbinom(n=rep(1,10),size=1,prob=c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25)))

scores<-colSums(test)/10

library(ggplot2)
qplot(scores)+
  geom_histogram()

length(scores[scores>=.75])/10000

```
Question 3b asks "... to receive 75% or greater on this test", however the solution video shows only greater than. I am showing equal to or greater than in my solution, in line with the question rather than the solution video.

Confidence: ~.80 for questions 1 & 2, 0 for question 3.
           
           