---
title: "Lab8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1
```{r}

zscorefunction<-function(raw,mu,sdev){
  zscore<-(raw-mu)/sdev
  return(zscore)
}

##demonstrate function works properly:

random_data<-c(2,5,10,3,6)
zscorefunction(random_data,4,2)

##convert raw scores to z scores:

zscorefunctionb<-function(raw,mu=NULL,sdev=NULL){
  if(is.null(mu)==TRUE) mu<-mean(raw)
  if(is.null(sdev)==TRUE) sdev<-sd(raw)
  zscore<-(raw-mu)/sdev
  return(zscore)
  }
zscorefunctionb(random_data,4,2)
zscorefunctionb(random_data)
  

```

#Question 2

```{r}

ztest<-function(sample_mean,sample_size,mu,sigma,two.tailed=TRUE){
  distribution_mean<-mu
  distribution_sd<-sigma/sqrt(sample_size)
  
p_value<-pnorm(sample_mean,distribution_mean,distribution_sd, lower.tail = FALSE)

if(two.tailed==TRUE) p_value<-p_value*2
return(p_value)
}

ztest(sample_mean=50,sample_size=25,mu=40,sigma=7,two.tailed=TRUE)



##Observed value larger than sample mean
ztest<-function(sample_mean,sample_size,mu,sigma,two.tailed=TRUE){
  
    distribution_mean<-mu
    distribution_sd<-sigma/sqrt(sample_size)
    
    abs_diff<-abs(sample_mean-mu)
  
    p_value<-pnorm((mu+abs_diff),sample_mean,distribution_mean,distribution_sd, lower.tail = FALSE)

  if(two.tailed==TRUE) p_value<-p_value*2
  return(p_value)
    
}

ztest(sample_mean=37,sample_size=5,mu=40,sigma=7,two.tailed=FALSE)



```

For the first function: 
We found that the probability of obtaining a sample mean of 50 for a sample with 25 scores, taken from a distribution with mean 40 and standard deviation 7 is 9.14e-13. This is a very small probability; there is a very small chance of observing a mean of 50 for a sample of this size. 


There is an issue with my second function in problem 2 that I am struggling with troubleshooting - I get an incorrect, negative value (obviously, this value cannot logically be negative). The function seems to run smoothly, which makes it difficult to pinpoint where the issue lies. I will continue to try to figure it out and re-watch the solution video, but I wanted to note this in case you are able to see the source of the issue. 