---
title: "Lab9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Original Results

"16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, χ2(19,N = 21) = 18.24, p = .506, and χ2(1, N = 21) = 0.15, p = .696, respectively."

##Replication of results
```{r}

data <- read.csv(file="Lab9Data.csv")

##Restrict data to experiment 1a only
library(dplyr)
exp1data<-data%>%
  filter(ExperimentNumber==1)

##two-tailed binomial test (testing infants' choice of novel toy)
##c=novel toy

sum_C<-sum(exp1data$Infant.Chose.C)
NumInfants_C<-length(exp1data$Infant.Chose.C)

(binomial_p<-pbinom(q=NumInfants_C-sum_C, size=NumInfants_C, prob=.5, lower.tail = TRUE)*2)

##Chi-square for gender

library(tidyr)

gender_table<-exp1data %>%
  group_by(Gender, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from=c(Gender),values_from=counts)

gender_table<-gender_table[,2:3]

(gender_chisq<-chisq.test(gender_table))
(uncorrected_chisq<-sum((gender_chisq$observed
                        -gender_chisq$expected)^2
                       /gender_chisq$expected))

gender_chisq_unc<-pchisq(uncorrected_chisq,1,lower.tail = FALSE)

##Chi-square for age

age_table<-exp1data %>%
  group_by(AgeMonths, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from=c(AgeMonths),values_from=counts)

age_table[is.na(age_table)]<-0
age_table<-as.matrix(age_table[,2:21])

(age_chisq<-chisq.test(age_table))

```

#Original Report

However, in the critical test trial that followed, 16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage
significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, χ2(19, N = 21) = 18.24, p = .506, and χ2(1, N = 21) = 0.15, p = .696, respectively.

#Reproduced Report

However, in the critical test trial that followed, `r sum_C` of `r NumInfants_C` infants (`r round((sum_C/NumInfants_C)*100,digits=1)`%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `r round(binomial_p,digits=3)`, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$(`r round(age_chisq$parameter,digits=3)`, N=  `r round (sum(age_chisq$observed),digits=3)`) = `r round (age_chisq$statistic,digits=2)`, p = `r round(age_chisq$p.value,digits=3)`, and $\chi^2$ (1, N = 21) = `r round (uncorrected_chisq,digits=2)`, p = `r round(gender_chisq_unc,digits=3)`, respectively.

#Conclusions

Our results match the results reported by the authors. There is only a slight difference in the p-value of the binomial test (reported by the authors as .026, compared to our obtained value of .027). This may be a rounding/reporting error on the authors end, especially if rounding was performed manually, and overall does not affect the conclusions drawn from this statistical test. 